Ants-Review: an Ethereum-Based Privacy-oriented Protocol for Incentiviced Open Peer Reviews

### 2020-11-23 article.tex
Commit by @naszam

\title{Ants-Review: an Ethereum-Based Protocol for Peer Reviews}

@@

Nazzareno Massari\inst{2}\orcidID{0000-0002-6638-2174}\thanks{Corresponding author}}

@@

\and Smart Contract Engineer, London, United Kingdom \\

>>>>

\title{Ants-Review: an Ethereum-Based Privacy-oriented Protocol for Incentiviced Open Peer Reviews}

@@

Nazzareno Massari\inst{2}\orcidID{0000-0002-6638-2174}\thanks{These authors equally contributed to this work.}}

@@

\and MakerDAO, Community Development, London, United Kingdom \\
